manuscript

### 2024-01-24 manuscript.rmd
Update manuscript.rmd

---
title: "manuscript"
editor: visual
bibliography: references.bib
output:
  word_document:
    reference_docx: "Masters-Thesis-and-Creative-Work-Template.docx"
csl: "marine-mammal-science.csl"
header-includes:
- \setlength{\parindent}{4em}
- \usepackage{setspace}\doublespacing
---

# Manuscript Draft

@@

## Results

@@

## Discussion

@@

## Acknowledgements

@@

2)  Environmental covariates (group by physiographic, oceanographic, etc)

@@

|------------------|------------------|--------------------|------------------|

@@

| Distance to shore (m)              | 0.01-Degree Grid | ERDAPP                                                                                                                                            |                                         |
| Distance to continental slope (m)  | 15 arc sec       | Derived from General Bathymetric Chart of the Oceans (GEBCO) @weatherall2015                                                                      | @barlow2009                             |
| Bathymetric slope (°)              | 15 arc sec       | Derived from GEBCO tif                                                                                                                            | @becker2010 @virgili2022                |
| Depth (m)                          | 15 arc sec       | ERDAPP                                                                                                                                            | @forney2012 @becker2010 @virgili2022    |
| Wind curl stress                   | 1°, 6-hourly     | ERDDAP                                                                                                                                            | @mannocci2015                           |
| Mixed layer depth (m)              | 0.08°, 3-hourly  | HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. | @mccullough2021, @forney2012 @moore2021 |
| Thermocline temperature (°C)       | 0.08°, 3-hourly  | HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. | @mccullough2021                         |
| Thermocline depth (m)              | 0.08°, 3-hourly  | HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. |                                         |

@@

| Salinity at 400m                   | 0.08°, 3-hourly  | HYCOM + NCODA, GLBy0.08/expt 93.0                                                                                                                 |                                         |
| Temperature at 400m (°C)           | 0.08°, 3-hourly  | HYCOM + NCODA, GLBy0.08/expt 93.0                                                                                                                 |                                         |
| SST mean                           | 0.01° , daily    | ERDAPP                                                                                                                                            | Becker 2007, @forney2012 @virgili2022   |
| CHL                                | 4 km, monthly    | ERDAPP                                                                                                                                            | @forney2012 @virgili2019                |
| Sea Surface Height Anomalies (m)   | daily            | ERDAPP                                                                                                                                            | @virgili2019                            |

>>>>

---
title: "manuscript"
editor: visual
bibliography: references.bib
header-includes:
- \setlength{\parindent}{4em}
- \usepackage{setspace}\spacing{2}
output:
  word_document:
    reference_docx: "Masters-Thesis-and-Creative-Work-Template.docx"
csl: "marine-mammal-science.csl"
---

@@

~~"The Tweedie is a family of exponential type distributions, which are tolerant to large numbers of zero observations (Candy 2004)." -- Lacey and Hammond 2023~~

(Candy, S.G. 2004. Modeling catch and effort data using Generalised Linear Models, the Tweedie Distriution, Random Vessel Effects and Random Stratum-by-Year effects. CCAMLR Sci. 11: 59--80.)

## Results (moved to Google Drive)

@@

## Discussion (moved to Google Drive)

@@

## Acknowledgements (moved to Google Drive)

@@

2)  List of environmental predictor covariates with resolution, data source, and justification. \

+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+

@@

+=====================================+==================+=======================================================================================================================================================+=========================================+

@@

+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Distance to escarpment (m)          | 30 arc sec       | (D) Calculated from : Global Seafloor Geomorphic Features Map\                                                                                        | Lacey and Hammond, 2023                 |
|                                     |                  | P.T. Harris, M. Macmillan-Lawler, J. Rupp, E.K. Baker, Geomorphology of the oceans, #Marine Geology, Volume 352, 2014, Pages 4-24, ISSN 0025-3227,    |                                         |
|                                     |                  | <https://doi.org/10.1016/j.margeo.2014.01.011>.                                                                                                       |                                         |
|                                     |                  | (<https://www.sciencedirect.com/science/article/pii/S0025322714000310>)                                                                               |                                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Distance to shore (m)               | 0.01-Degree Grid | (A) ERDAPP                                                                                                                                            |                                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Distance to continental slope (m)   | 15 arc sec       | (C) Derived from General Bathymetric Chart of the Oceans (GEBCO) @weatherall2015                                                                      | @barlow2009                             |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Bathymetric slope (°)               | 15 arc sec       | (C) Derived from General Bathymetric Chart of the Oceans (GEBCO) @weatherall2015                                                                      | @becker2010 @virgili2022                |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Depth (m)                           | 15 arc sec       | (A) ERDAPP                                                                                                                                            | @forney2012 @becker2010 @virgili2022    |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Wind curl stress                    | 1°, 6-hourly     | (A) ERDDAP                                                                                                                                            | @mannocci2015                           |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Mixed layer depth (m)               | 0.08°, 3-hourly  | (B) HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. | @mccullough2021, @forney2012 @moore2021 |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Thermocline temperature (°C)        | 0.08°, 3-hourly  | (B) HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. | @mccullough2021                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Thermocline depth (m)               | 0.08°, 3-hourly  | (B) HYCOM + NCODA, GLBy0.08/expt 93.0, calculated with variable representative isotherm method (Fiedler 2010), as described in McCullough et al 2021. |                                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+

@@

+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Salinity at 400m                    | 0.08°, 3-hourly  | (B) HYCOM + NCODA, GLBy0.08/expt 93.0                                                                                                                 |                                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Temperature at 400m (°C)            | 0.08°, 3-hourly  | (B) HYCOM + NCODA, GLBy0.08/expt 93.0                                                                                                                 |                                         |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Sea Surface Temperature (mean) (°C) | 0.01° , daily    | (A) ERDAPP                                                                                                                                            | Becker 2007, @forney2012 @virgili2022   |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Chlorophyll-a (mean) (mg m-3)       | 4 km, monthly    | (A) ERDAPP                                                                                                                                            | @forney2012 @virgili2019                |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+
| Sea Surface Height Anomalies (m)    | daily            | (A) ERDAPP                                                                                                                                            | @virgili2019                            |
+-------------------------------------+------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------+

\*\* Distances were calculated in R. Source A: ERDAPP (add link); Source B: HYCOM + NCODA, GLBy0.08/expt 93.0 (add link); Source C: General Bathymetric Chart of the Oceans (GEBCO, add link); Source D: Global Seafloor Geomorphic Features Map (add link).
